\input{../header2.tex}

\chapter*{ABSTRACT}
\addcontentsline{toc}{chapter}{Abstract}
\noindent
An industrial robot is isolated into work cells 
making the operation of industrial robots rigid and inflexible. The robot
requires tremendous amount of time and resources should a new task or change is required in 
the work-cell. 
This stigma and the reality of owning an industrial robot hinder the confidence of \acrfull{SME}
to adopt industrial robot technology. This thesis attempts to democratize robot 
technology and automation to the SMEs by introducing an inexpensive, flexible, and safe
robotic technology.
This thesis intends to show the feasibility of
constructing a robot manipulator with obstacle avoidance motion planning. 
Therefore, 
a six-axis 
manipulator as a prototype is developed to investigate the planning and motion control of the manipulator 
  in a dynamic environment.  
  The prototype replicates the typical 6R industrial robot design. \acrfull{RRT} is chosen to plan and control 
the motion of the manipulator in the dynamic environment. 
A physic engine simulator simulates the manipulator and 
the  obstacle avoidance planning.
A \acrfull{3D} obstacle is introduced into the simulation environment
and moves periodically from an initial
point to a goal point in the form of 
sinusoidal motion described by $A+B\sin{(2\pi tC)}$. 
The motion planning
is validated with the prototype hardware. However, the moving 
  obstacle is augmented by the simulation environment to maintain safe experimentation 
  and the preservation of the prototype. It is observed that
  the global planner, RRT, behaves reactively when subjected to the cycle space
  defined in this report.  
  Consequently, \acrfull{RTAB-Map} is used to facilitate an encoder-less context 
of the manipulator. 
Although RTAB-Map provides the confident state estimation 
  of the robot task space and, consequently, the joint-space configuration
  of the manipulator, the estimation is intermittent.
It is recommended that a new pipeline, 
capable of splining between the state estimation and the planning trajectories, is
  implemented for motion planning in the dynamic environment using \acrfull{SLAM} solutions under the encoderless context.
\newpage
\input{../end.tex}
