\input{../header2.tex}
\chapter{Conclusion And Recommendation}
\label{chap:conclusion_recommendation}

\section{Conclusion}
    In this research, a prototype of an industrial robot is 
    developed to investigate the planning and motion control 
    of the manipulator for compliant usage in an industrial 
    setup.

    The robot is as 6R manipulator, with six-degree-of-freedom. Each joints is actuated 
    with Dynamixel servo and are back-drivable. The end-effector is equipped with 
    an RGB-D sensor. The robot is named \rimini~. 
    
    Since the Dynamixel motors are not supplemented with a mathematical model, the joints
    are controlled based on time-parameterized controller where, the set up of each of
    the motor's velocity profile depends on the angular velocity limits and the angular
    acceleration limit. The time-parameterized controller was successfully tuned with informed velocity-acceleration limit
    parameterization. All of the \rimini~   controllers
    parameters and system configuration, including it's driver, are package as 
    a stack of ROS packages.

A benchmark was done to ascertain the best sampling-based planner for the \rimini~'s 
capability to avoid moving obstacles. The simulation for the benchmark considers a
static object, placed in the manipulator's workspace. 
RRT was selected given it's
rapid processing time, 0.031 s, at solving a planning objective. 
Two simulations were done; the first involved  
introducing a static object with 
unpredictable shape and placement 
into the manipulators line of motion, and the second 
simulation setup involve a moving object with the shape of a cylinder that was placed and moved in the robot's workspace.

Both the simulations were validated with \rimini~ hardware. 
The unpredictable static object invoked reactive motion 
correction, where no collision were reported.  
However, when moving obstacles were introduced, the replanning
fail to provide collision-free solution. The robot capability to avoid the moving obstacle, although less successful,
has not been consistent. The avoidance fails if
the RRT is invoke when the obstacle nearly approaching the $C_{cycle}$.

Although the performance of the RRT on a dynamic 
obstacle imposed under the cyclical space prescribed in algorithm \ref{algo:cycle_space}, 
is not satisfactory, the result shows that the robot
is capable at reacting to an obstacles when the obstacle 
is moving.
    
    This thesis's SLAM implementation, by repurposing
RTAB-Map as the SLAM framework and PHASER repurposing as the state estimation pipeline of the RTAB-Map, 
shows an intermittent and sparse estimation of the $C_{ee}$ which fails to 
continuously estimate the joint-configuration of the manipulator. 


\section{Recommendation for Future Works}
This thesis recommends a future work on improved state estimations of the 
RTAB-Map where the singularities reading during state estimation can be pass to
a splining process. The splining would consider the last reading of the RTAB-Map 
estimation pipeline at, $t_{last}$, and the output from the 
\textit{equation \ref{eq:splining_traj_selection}},

\import{\thesisDir/chapter6/equations/}{splining_traj_selection.tex}

where $\hat{C}_{last}$ is the last state estimation of the RTAB-Map before data silence.
This approach has the potential of providing pseudo-continuous streaming of feedback for
joint controllers; follow-joint-trajectory controller in ROS
being the immediate candidate for an encoder-less context. The implication
is an encoder-less system that requires no encoders as feedback and, hence, reduces
the cost, space of the robot design, and the market price for commercialization of
affordable automation system to SME's. 

\input{../end.tex}
