\documentclass[a4paper, 10pt]{article}
\title{Repurposing a Sampling-Based Planner for a Six-Degree-of-Freedom Manipulator to Avoid Synthetic Moving Obstacles}

\usepackage{authblk}

%small text for affilliation
\renewcommand\Affilfont{\itshape\small}

\author[1]{Hafiz Iman}
\author[1]{Raisuddin Khan}

\affil[1]{Department of Mechatronics Engineering, Kulliyah of Engineering, International Islamic University Malaysia}
  
%formattingi
  \newcommand\thisPaperDir{/home/asl/version-control/ws_thesis/writing_papers/resampling_planning_in_dynamic_environment}
  \newcommand\thesisDir{/home/asl/version-control/ws_thesis/thesis_latex}
  \usepackage{import}
  %\usepackage{natbib}
  \usepackage[backend=biber,bibencoding=utf8,style=ieee]{biblatex}
  \addbibresource{\thesisDir/bibtex/library.bib}
	\usepackage{soul,color}
  \usepackage{pdflscape} %for changing page orientation
  \usepackage[shortlabels]{enumitem}
  \usepackage{amssymb}
  \usepackage{graphicx} %for inserting photo
  \usepackage{subcaption}
  \usepackage{amsmath} % for equations
  \DeclareMathOperator*{\argmax}{argmax} % for underword argmax

  \usepackage{mathtools} % for equations
  \usepackage{physics}
  \usepackage{arydshln} %adding dash line to matrix

  \usepackage{float}  %deactivate this if hyperref does not work with algo
  \usepackage{hyperref}
  \usepackage{tocbibind}  
  \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
  \usepackage{titlesec} %for deeper subsections
  \usepackage{multirow} %for merging row in cell
  \setcounter{secnumdepth}{4} %setting subsection 4 section deep
  % numbering equations
  \numberwithin{equation}{section} %equation number based on chapter

  \usepackage{xfrac} % for fraction in the for n/d
  \usepackage{esint} % for easy integral symbols

  %for listing algorithms from algorithm2e
  \newcommand{\listofalgorithmes}{\tocfile{\listalgorithmcfname}{loa}}
  %for footnote
  \renewcommand{\thefootnote}{\fnsymbol{footnote}}

  % for formattgin algorithm2e box [iman] I have to put after listofalgorithmes
  \newcommand\mycommfont[1]{\footnotesize\ttfamily\textcolor{blue}{#1}}
  \SetCommentSty{mycommfont}
  \SetKwInput{KwInput}{Input}                % Set the Input
  \SetKwInput{KwOutput}{Output}              % set the Output

  % This command is useful when importing subdirectory items

%  \input{\thesisDir/style.tex}
%margin
\usepackage{setspace}
\usepackage[
  a4paper,
  left=3.8cm,
  right=2.5cm,
  top=2.5cm,
  bottom=3cm,
  footskip=1.7cm
]
{geometry}

%chapter section style
\usepackage{titlesec} %for deeper subsections and changing chpt sec style
\titleformat{\chapter}
   [display] %possible values are hang, leftmargin, drop, etc.
   {\fontsize{14}{16}\bfseries\centering} % format to be applied to the whole title
   {\MakeUppercase{\chaptertitlename} \thechapter} %label setting
   {24pt} %horizontal separation between label and title body
   {\MakeUppercase} %code preceding the title body
   \titlespacing{\chapter}{0pt}{0pt}{48pt} %4spacing after title


\setcounter{secnumdepth}{4} %setting subsection 4 section deep
%paragraph
\parindent=12mm


%header style
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}

%making sure table and figures caption is 1 single spacecaption is 
%make sure that the tables are not in \center environment
%it will add more space between caption and the table/figures
\usepackage{caption}
\captionsetup[table]{skip=12pt}
  % This command is for keywords
  \providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}

  \date{} %setting date as empty string so no date shown in the article

  \newcommand\rimini[0]{\textit{r\_mini}} %r_mini typesetting

  %subfigure referecing

\begin{document}
{\let\newpage\relax\maketitle}
\begin{abstract}
  This paper presents the use of a sampling-based planner 
  as a local planning scheme
  to avoid obstacle between a robotic arm and a moving obstacle.
  Based on a planner benchmark on a obstacle-ridden environment,
  rapidly-exploring random tree (RRT) planner are used to 
  populate the trajectories of the
  task space and map them into a configuration space using
  Newton-Raphson-based inverse kinematic solver.
  Three robot poses are defined in a cycle of back-and-forth motion; 
  the starting, the midpoint, 
  and the end pose. The starting pose and the end pose are equal.
  The robot repeatedly moves from the starting pose to the end pose via the 
  midpoint pose. Poses between the three are a subset of a trajectory populated 
  by the sampling-based planner. Each set of trajectory is unique. 
  We impose
  periodically occuring synthetic obstacle that moves in and out of 
  the robot arm workspace defined in a simulated environment. 
  Within the robot's workspace, 
  the obstacle moves and cuts through the cyclical space to emulate a 
  dynamic environment. Based on the performance of the local
  planning strategy, the robot has a higher success in
  avoiding the obstacles when the planning query starts during the presence of 
  the obstacles in the cyclical space. However, a higher chance of collision
  occurs when the planning query is invoked when the obstacle nearly 
  approaches the cyclical space.
\end{abstract}

\keywords{mechatronics, robotics, planner, path-planning, sampling-based planner, robotic arm, manipulator, dynamic environment, moving obstacles, ROS, MoveIt}

\section{Introduction}
\cite{Hagele2016}


\clearpage
\printbibliography

\end{document}


