\input{../header2.tex}

\chapter*{ACKNOWLEDGEMENTS}
\addcontentsline{toc}{chapter}{Acknowledgements}
All glory to the Lord, Allah the Almighty. This research has taught me so much. I have been
at my lowest and highest within this endeavor, and of all people that help me with my bearing,
none so important as my supervisor, Prof. Dr. Md Raisuddin Khan for taking a chance on me
and my concept, and for supporting me endlessly throughout of this research. 
I thank you and appreciate you and your trust.
I hope someday, I could do the same to another brilliant, yet so broken, 
scholar who only need just one person to help him/her/they shine so bright. 

I would be remissed if I did not mention my beautiful family; my mother, Jimelah, my father, Iman and
my brother, Fariz. Thank you for being so patient througout the time I attempt to make this research 
a successful one. You have been my rock, and will always be my home. 

Richard Herman Wallis, the hero of my life and the backbone
of this thesis and myself; I cannot thank you enough for always being 
there to pick me up when I had fell so low.

To my dearest and closest friends, Kirunnisa and Akbar, thank you for the long chats and for being
my moral compass. You both are the most beautiful person that 
I have ever met, inside and out.

To my vai from another mother, (Prof.) Nayeem-vai, thank you so much for being 
present this whole time when I needed your opinion, your wake-up calls, and your 
sense of humor. I hope I get to see you again and make robots together this time!

I would also like to thank everyone in the Department of Mechatronics Engineering for
being the best example of professionalism. Thank you Dr. Ali Sophian, for having my back and 
for your vote of confidence.

I also would like to express my gratitude to Ankit-sensei, and Emaru-sensei who brought me 
in and showed how a world-class institution works and contributes to research and science. 

\input{../end.tex}
